---
name: Alexander G. Guldbrand
date: "`r format(Sys.time(), '%B, %Y')`"
address: |
         | Vigerslevvej 344, 1. tv., 2500 Valby, Denmark
         | Nationality: Danish, Date of birth: 17/03/1991
profilepic: pic.png
email: alexguldbrand@gmail.com
phone: 25 17 03 76
github: Gulde91
linkedin: Alexander-Guldbrand
headcolor: 414141
output: vitae::awesomecv
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

\vspace{0.2cm}

# About Me
*write something relevante..*

# Professional Experience
```{r}
library(tibble)
arb <- tribble(
    ~ansvar, ~startYear, ~endYear, ~rolle, ~sted, ~beskriv,
    "Tasks", 2016, "now", "Data Scientist", "Udviklings- og Forenklingsstyrelsen", 
    "Development and deployment of supervised and unsupervised models through R",
    "Tasks", 2016, "now", "Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Team lead Data Scientist on machine learning models developed in the VAT area",
    "Tasks", 2016, "now", "Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Ensure code quality through code review, unit tests and reproducible code ",
    "Tasks", 2016, "now", "Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Cooperating with the Scandinavian countries in advanced analytics on the VAT area",
    "Tasks", 2016, "now", "Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Recruiting new employees",
    "Tasks", 2014, "2016", "Junior Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Analyzing citizens and companies contack flow with SKAT",
    "Tasks", 2014, "2016", "Junior Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Analyzing citizens behavior on tastselv.dk",
    "Tasks", 2014, "2016", "Junior Data Scientist", "Udviklings- og Forenklingsstyrelsen",
    "Clustering citizens and companies regarding to money transfer to foreign countries"
)

arb %>%
  detailed_entries(
    with = rolle,
    what = ansvar,
    why = beskriv,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = sted
  )
```


# Education
```{r}
udd <- tribble(
    ~ansvar, ~startYear, ~endYear, ~rolle, ~sted, ~beskriv,
    "Final result: 11,6", 2014, 2016, "Cand.merc.(mat.)", "Copenhagen Business School",
    "Multivariate Statistical Models (12)",
    "Final result: 11,6", 2014, 2016, "Cand.merc.(mat.)", "Copenhagen Business School",
    "Big Data Analytics (10)",
    "Final result: 11,6", 2014, 2016, "Cand.merc.(mat.)", "Copenhagen Business School",
    "Data Science: Data Driven Decision Making (12)",
    "Final result: 11,6", 2014, 2016, "Cand.merc.(mat.)", "Copenhagen Business School",
    "Practical Time Series Analysis (12)",
    "Final result: 11,6", 2014, 2016, "Cand.merc.(mat.)", "Copenhagen Business School",
    "Master's thesis - Customer segmentation in Danske Bank (12)",
    "Final result: 9,0", 2011, 2014, "HA(mat.)", "Copenhagen Business School", NA,
    NA, 2007, 2010, "Natural Science/Mathematical student", "Marie Kruse Skole", NA
)

udd %>%
  detailed_entries(
    with = rolle,
    what = ansvar,
    why = beskriv,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = sted
  )
```

# Courses and Projects
<!-- # futher education or courses, books and selfmade projects
2020 Deep Learning Specialization, deeplearning.ai, Coursera
“Specialization”.
Five course specialization covering among other things hyperparameter tuning, regularization, optimization algorithms, CNNs and RNNs

"En serie på 5 kurser som både dækker grundlæggende, men også mere specialiseret viden om deep learning. Kurset berører primært CNNs og RNNs.",

-->
```{r, eval=TRUE}
# Coursera
tribble(
    ~rolle, ~ansvar, ~startYear, ~endYear, ~beskriv,
    "Deep Learning Specialization", "deeplearning.ai, Coursera", 2018, 2019,
    "A series of 5 courses with covers basic but also more specialized knowledge about deep learning. This course is focusing on CNNs and RNNs.") %>% 
  detailed_entries(
    with = rolle,
    what = ansvar,
    why = beskriv,
    when = glue::glue("{startYear} --> {endYear}",.na = ""))

# DataCamp
tribble(
    ~rolle, ~startYear, ~endYear, ~beskriv,
    "DataCamp courses", 2018, "now",
    "Writing Efficient R Code, Defensive R Programming, Introduction to Natural Language Processing in R, Anomaly Detection in R, Introduction to Git, Introduction to Python, Python for R Users, Foundations of Functional Programming with purrr, Intermediate Functional Programming with purrr, Web scraping in R.") %>% 
  detailed_entries(
    with = rolle,
    what =  glue::glue("\\descriptionstyle{<beskriv>}", .open = "<", .close = ">"),
    when = glue::glue("{startYear} --> {endYear}",.na = ""), .protect = FALSE)

# komma model
tribble(
    ~rolle, ~startYear, ~endYear, ~beskriv,
    "Comma-model", 2019, 2020, "Development of a LSTM model to predict where a comma should be placed in a danish sentence.") %>% 
    detailed_entries(
    with = rolle,
    what =  glue::glue("\\descriptionstyle{<beskriv>}", .open = "<", .close = ">"),
    when = glue::glue("{startYear} --> {endYear}",.na = ""), .protect = FALSE)
```

<!--
# Relevante kompetencer
-->

# Skills
\renewcommand{\arraystretch}{1.5} <!-- definere linjeafstand -->
\begin{minipage}[t]{0.7\textwidth}
  \vspace{-\baselineskip}
  \entrypositionstyle{Technical skills} \\
  \begin{tabular}{llllll}
    \textbf{R} & \resume{2}{6} &
    \textbf{VBA} & \resume{2}{6} & 
    \entoure{\textcolor{white}{Git}} & 
    \entoure{\textcolor{white}{Regex}} \\
    \textbf{SQL} & \resume{2}{6} & 
    \textbf{Python} & \resume{2}{6} &
    \entoure{\textcolor{white}{Google Cloud}} &
    \entoure{\textcolor{white}{Jenkins}} \\
    \textbf{SAS} & \resume{2}{6} & & &
    \entoure{\textcolor{white}{Jira}} \\
  \end{tabular}\end{minipage}
\begin{minipage}[t]{0.3\textwidth}
  \vspace{-\baselineskip}
  \entrypositionstyle{Languages} \\
  \begin{tabular}{ll}
    \textbf{Danish} - Native \\
    \textbf{English} - Proficient \\
  \end{tabular}\end{minipage}
\renewcommand{\arraystretch}{1} <!-- definere linjeafstand -->

<!-- \newpage -->
# Additional Experience
<!-- overvej hvor relevant nedenstående er, og om det er relevant at have udbytte med --> 
```{r}
and <- tribble(
    ~ansvar, ~startYear, ~endYear, ~rolle, ~sted, ~beskriv,
    "Outcome:", 2010, 2014, "Receptionist", "Hotel Jørgensen", 
    "Cultural understanding",
    "Outcome:", 2010, 2014, "Receptionist", "Hotel Jørgensen", 
    "Personal service",
    "Outcome:", 2010, 2014, "Receptionist", "Hotel Jørgensen", 
    "Take care of unforeseen incidents",
    "Outcome:", 2009, 2011, "Football coach", "Farum Boldklub", 
    "To take responsibility for a group",
    "Outcome:", 2009, 2011, "Football coach", "Farum Boldklub", 
    "Defining ways to play and integrating it through training and match",
    "Outcome:", 2009, 2011, "Football coach", "Farum Boldklub", 
    "B1 Football coach education",
    "Outcome:", 2005, 2008, "Youth football player", "FC Nordsjælland", 
    "Understading for working in a professionel enviroment"
    )

and %>%
  detailed_entries(
    with = rolle,
    what = ansvar,
    why = beskriv,
    when = glue::glue("{startYear} --> {endYear}",.na = ""),
    where = sted
  )
```

